FraCaS: Temporal Analysis

### 2020-06-09 paper2020/paper.tex
typography

We treat verbs in the progressive form as different semantically. For
example, ``John was writing a book'' is encoded as
$∃t1, t2. t1<= t2, t2 <= now, PROG_write(John,book,t1,t2)$, while
``John wrote a book'' is encoded as
$∃t1, t2. t1<= t2, t2 <= now, write(John,book,t1,t2)$. This is
necessary, because $PROG_write$ is subject to
$\constant{subsumption}$: if John is writing in interval $[t1,t2]$
then he is writing in any subinterval. However, the same cannot be
said of $write$: the end-points of the interval indicates the time
needed to complete the achievement. (For example, John wrote a book in
1993 does not entail John wrote a book in March 1993.) Thus, $write$
is on the contrary subject to $\constant{unicity}$. Finally, we also
have $write(x,y,t1,t2) -> PROG_write(x,y,t1,t2)$. That is, the
achievement variant implies the stative variant, in the same interval.
Consequently we get the entailment from ``John wrote a book'' to
``John was writing a book''.

@@

% Things we cannot handle (I think): John was writing a book in 1991
% -> John wrote a book in 1991 (I think we predict entailment
% here). This is because there is no distinction with progressive and
% non progressive aspect. We did not do it, I guess because it was
% needed, but just for future reference. There are similar examples
% playing around with LEXICAL aspect (aspect grammatically encoded)
% that we could look at in future work

% Accomplishments usually involve a culmination point in the action
% which is necessary for the event to be completed. This is not
% necessary for activities. John stopped writing a book not-> John
% wrote a book (but does imply that John was writing a book), but,
% John stopped running -> John run and John was runnning

>>>>

We treat verbs in the progressive form as different semantically. For
example, ``John was writing a book'' is encoded as
$∃t1, t2. t1≤ t2, t2 ≤ now, PROG\_write(John,book,t1,t2)$, while
``John wrote a book'' is encoded as
$∃t1, t2. t1≤ t2, t2 ≤ now, write(John,book,t1,t2)$. This is
necessary, because $PROG\_write$ is subject to
$\constant{subsumption}$: if John is writing in interval $[t1,t2]$
then he is writing in any subinterval. However, the same cannot be
said of $write$: the end-points of the interval indicates the time
needed to complete the achievement. (For example, John wrote a book in
1993 does not entail John wrote a book in March 1993.) Thus, $write$
is on the contrary subject to $\constant{unicity}$. Finally, we also
have $write(x,y,t1,t2) → PROG\_write(x,y,t1,t2)$. That is, the
achievement variant implies the stative variant, in the same interval.
Consequently we get the entailment from ``John wrote a book'' to
``John was writing a book''.

@@

% Things we cannot handle (I think): John was writing a book in 1991
% → John wrote a book in 1991 (I think we predict entailment
% here). This is because there is no distinction with progressive and
% non progressive aspect. We did not do it, I guess because it was
% needed, but just for future reference. There are similar examples
% playing around with LEXICAL aspect (aspect grammatically encoded)
% that we could look at in future work

% Accomplishments usually involve a culmination point in the action
% which is necessary for the event to be completed. This is not
% necessary for activities. John stopped writing a book not→ John
% wrote a book (but does imply that John was writing a book), but,
% John stopped running → John run and John was runnning
